### 2024-07-15 manuscript/manuscript.qmd
updated MS

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$| Prediction interval
|:------------|:----------|:--------  --------------|:----|:-----|:-----|:------|
| Valence All |           | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim|           | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   |           | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  |           | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 24,15660  | 0.6585 [0.5574; 0.7404] | 7.44|.0001 | 0.142| 97.9% |
| Val. MaxTrim|   13,7363 | 0.6489 [0.5980; 0.6945] | 18.5|.0001 | 0.008| 88.5% |
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     |            | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim|            | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   |            | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  |            | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 24,15660   | 0.8070 [0.7453; 0.8550] | 10.3|0.0001|0.155 | 96.8%  | 0.2258; 0.9648
| Aro.Max.Trm | 14,12061   | 0.8182 [0.8021; 0.8331] | 25.6|0.0001|0.0132| 96.8%  | 0.6372; 0.9047

| *N Features*|            |          |              |     |      |      |       |   
| <18 F       |            |          |              |     |      |      |       |
| 18-260 F    |            |          |              |     |      |      |       |
| 260+ F      |            |          |              |     |      |      |       |
| *Techniques*|            |          |              |     |      |      |       |  
|   KS        |            |          |              |     |      |      |       |
|   LM        |            |          |              |     |      |      |       |
|   FD        |            |          |              |     |      |      |       |
|   NN        |            |          |              |     |      |      |       |
|   RF        |            |          |              |     |      |      |       |

>>>>

| Concept     | Models, obs|$r$ [95%-CI]            | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:----------|:------------------------|:----|:-----|:-----|:------|
| Valence All |           | 0.6137 [0.5540; 0.6672] | 15.9|.0001 | 0.092| 98.1% |
| Valence Trim|           | 0.6048 [0.5920; 0.6172] | 72.4|.0001 | 0.0007| 33.1%|
| Valence M   |           | 0.6038 [0.4671; 0.7124] | 7.83|.0001 | 0.100| 97.8% |
| Valence Md  |           | 0.6018 [0.4659; 0.7099] | 7.87|.0001 | 0.098| 97.7% |
| Valence Max | 24,15660  | 0.6585 [0.5574; 0.7404] | 7.44|.0001 | 0.142| 97.9% |
| Val. MaxTrim|   13,7363 | 0.6489 [0.5980; 0.6945] | 18.5|.0001 | 0.008| 88.5% |
| *N Features*|           |                         |     |      |      |       |
| <18 F       |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 18-260 F    |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| 260+ F      |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
| *Techniques*|           |                         |     |      |      |       |
|   KS        |           | 0.3606 [0.3201; 0.3997] | xxxx|.xxxx | 0.xxx| XXXX% |
|   LM        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   FD        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   NN        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |
|   RF        |           | 0.xxxx [0.xxxx; 0.xxxx] | xxxx|.xxxx | 0.xxx| XXXX% |

@@

| Concept     | Models, obs|$r$ [95%-CI]             | $t$ | $p$  |$\tau^2$|$I^2$|
|:------------|:-----------|:------------------------|:----|:-----|:-----|:------|
| Arousal     |            | 0.7959 [0.7666; 0.8218] |29.0 |0.0001|0.0676|95.6%  |
| Arousal Trim|            | 0.7932 [0.7846; 0.8014] | 96.5|0.0001|0.0030|73.3%  |
| Arousal M   |            | 0.7567 [0.6752; 0.8199] | 12.7|0.0001|0.0739|95.6%  |
| Arousal Md  |            | 0.7627 [0.6819; 0.8252] | 12.7|0.0001|0.0757|95.3%  |
| Arousal Max | 24,15660   | 0.8070 [0.7453; 0.8550] | 10.3|0.0001|0.155 | 96.8% | 
| Aro.Max.Trm | 14,12061   | 0.8182 [0.8021; 0.8331] | 25.6|0.0001|0.0132| 96.8% | 
| *N Features*|            |          |              |     |      |      |       |   
| <18 F       |            |          |              |     |      |      |       |
| 18-260 F    |            |          |              |     |      |      |       |
| 260+ F      |            |          |              |     |      |      |       |
| *Techniques*|            |          |              |     |      |      |       |  
|   KS        |            |          |              |     |      |      |       |
|   LM        |            |          |              |     |      |      |       |
|   FD        |            |          |              |     |      |      |       |
|   NN        |            |          |              |     |      |      |       |
|   RF        |            |          |              |     |      |      |       |
